---
title: "Visuals"
output: github_document
date: "2023-02-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required Packages

```{r}
library(tidyverse)
library(dplyr)
library(ggpattern)
library(mapproj)
```

## Data Loading

First, we load in the `world_map` data set included embedded within the ``ggplot2` package. We do this by assigning it as an object within our environment:

```{r}
world_map <- ggplot2::map_data("world")
```

From here, we need to update `ggplot2::map_data('world')` to be compatible with datasets using ISO country codes. We can accomplish this by using this tutorial provided by Haslam (2021): https://rpubs.com/Thom_JH/798825.

The essential components required for this project are outlined sequentially in the code chunks below.

```{r}
world_map2 <- world_map %>% 
  rename(country = region) %>%
  mutate(country = case_when(country == "Macedonia" ~ "North Macedonia" ,
  country == "Ivory Coast"  ~ "Cote d'Ivoire",
  country == "Democratic Republic of the Congo"  ~ "Congo, Dem. Rep.",
  country == "Republic of Congo" ~  "Congo, Rep.",
  country == "UK" ~  "United Kingdom",
  country == "USA" ~  "United States",
  country == "Laos" ~  "Lao",
  country == "Slovakia" ~  "Slovak Republic",
  country == "Saint Lucia" ~  "St. Lucia",
  country == "Kyrgyzstan"  ~  "Kyrgyz Republic",
  country == "Micronesia" ~ "Micronesia, Fed. Sts.",
  country == "Swaziland"  ~ "Eswatini", 
  country == "Virgin Islands"  ~ "Virgin Islands (U.S.)", 
  TRUE ~ country))
```

```{r}
match_names <- c("Antigua" , "Barbuda", "Nevis", "Saint Kitts", "Trinidad", "Tobago", "Grenadines", "Saint Vincent")
```

```{r}
map_match <- world_map2 %>% 
  filter(country %in% match_names)
```

```{r}
map_match %>% distinct(country)

ant_bar <- c(137 ,138 )

kit_nev <- c(930 , 931)

tri_tog <- c(1425, 1426)

vin_gre <- c(1575, 1576, 1577)
```

```{r}
new_names_ref <- c("Antigua and Barbuda", "St. Kitts and Nevis","Trinidad and Tobago", "St. Vincent and the Grenadines")
```

```{r}
map_match <- map_match %>% 
  mutate(country = case_when(group %in% ant_bar ~ "Antigua and Barbuda",group %in% kit_nev  ~ "St. Kitts and Nevis" ,group %in% tri_tog  ~ "Trinidad and Tobago" ,group %in% vin_gre ~ "St. Vincent and the Grenadines") ) %>% 
  tibble()
```

```{r}
map_match %>% head()

map_match %>% 
  distinct(country)%>% 
  knitr::kable(caption = "Add to World Map")

map_match %>% 
  group_by(country) %>% 
  count(group)  %>% 
  knitr::kable(caption = "Add to World Map")

map_match %>% 
  str()
```


```{r}
world_map2 %>% 
  str()

world_map2 <-  world_map2 %>%
  filter(!country %in% match_names)

world_map2 <- world_map2 %>% 
  bind_rows(map_match) %>%
  arrange(country)  %>%
  tibble()

world_map2 %>% 
  filter(country %in% match_names)

world_map2 %>% 
  filter(country %in% new_names_ref) %>%
  group_by(country) %>%
  slice_max(order, n = 1)
```

```{r}
sub_sleeps <- c("Hong Kong", "Macao")

hk_mc <- world_map2 %>% 
  filter(subregion %in% sub_sleeps)

hk_mc <- hk_mc %>%
  mutate(country = case_when(subregion == "Hong Kong" ~ "Hong Kong, China" ,
  subregion == "Macao" ~ "Macao, China" ))

hk_mc %>% 
  slice(38:41) %>% 
  knitr::kable(caption ="Check structure")
```

```{r}
world_map2 <-   world_map2 %>%
  filter(!subregion %in% sub_sleeps)

world_map2 <- world_map2 %>% 
  bind_rows(hk_mc) %>%
  select(-subregion) %>% 
  tibble()
```

## Mapping choropleths for each primary outcome variable

Mean population-level water footprint dividends: 

```{r}
ggplot(world_map2, aes(x=long,y=lat,group=group,fill=country)) + 
  geom_polygon(color="black",alpha=.8,linewidth=.1) + 
  scale_fill_manual(values=c("lightcyan1","lightcyan2","lightcyan3","white","white","white","white","white","lightcyan1","paleturquoise4","lightcyan2","white","white","lightcyan4","lightcyan2","lightcyan2","white","white","white","white","lightcyan2","lightcyan2","lightcyan2","lightcyan2","lightcyan2","lightcyan2","white","white","white","lightcyan2","lightcyan1","darkslategray","lightcyan2","lightcyan2","lightcyan2","white","lightcyan2","lightcyan2","lightcyan3","white","lightcyan1","white","lightcyan1","white","white","lightcyan2","darkslategray","white","white","lightcyan1","white","lightcyan1","white","white","lightcyan2","lightcyan1","lightcyan2","white","white","lightcyan2","lightcyan2","lightcyan2","white","white","white","lightcyan1","paleturquoise4","lightcyan1","white","white","lightcyan2","white","lightcyan1","white","white","lightcyan2","lightcyan2","lightcyan4","white","white","white","white","lightcyan2","lightcyan1","lightcyan4","lightcyan2","lightcyan3","white","white","white","white","lightcyan1","white","white","white","lightcyan2","white","white","lightcyan1","lightcyan2","lightcyan2","lightcyan2","lightcyan1","lightcyan1","lightcyan4","white","lightcyan2","white","lightcyan2","lightcyan4","lightcyan2","lightcyan2","white","lightcyan2","lightcyan3","lightcyan1","white","white","lightcyan2","lightcyan2","white","lightcyan2","lightcyan2","white","white","white","white","lightcyan2","lightcyan2","lightcyan2","lightcyan1","white","lightcyan2","lightcyan2","lightcyan2","lightcyan2","lightcyan2","white","white","lightcyan2","lightcyan2","white","paleturquoise4","white","lightcyan1","white","white","lightcyan2","white","lightcyan3","white","white","lightcyan1","white","lightcyan2","lightcyan2","white","lightcyan2","lightcyan1","lightcyan2","white","white","white","white","lightcyan2","white","lightcyan2","lightcyan2","lightcyan1","white","white","lightcyan2","white","lightcyan2","lightcyan2","lightcyan1","white","lightcyan3","lightcyan2","white","white","white","lightcyan2","cadetblue4","lightcyan1","white","white","white","white","white","white","white","lightcyan1","lightcyan3","lightcyan1","lightcyan2","white","white","white","white","white","white","lightcyan1","lightcyan2","white","white","lightcyan2","white","lightcyan4","white","white","lightcyan4","lightcyan1","white","white","white","white","lightcyan2","lightcyan2","lightcyan2","white","lightcyan2","white","lightcyan1","lightcyan2","white","lightcyan1","white","white","lightcyan2","darkslategray","white","white","lightcyan1","lightcyan2","white","lightcyan3","darkslategray","lightcyan2","white","lightcyan2","white","lightcyan3","white","white","white","white","lightcyan1","lightcyan1","lightcyan1")) +
  xlab(" ") + 
  ylab(" ") + 
  guides(fill="none") +
  ggtitle("Figure 1. Choropleth map showing the mean anticipated poulation-level reductions in diet-attributable water use for each of the 133 included countries.") +
  theme(panel.background=element_rect(fill="aliceblue"),panel.border=element_rect(fill=NA),axis.ticks=element_blank(),axis.text=element_blank(),panel.grid=element_blank())
```

Mean population-level carbon footprint dividends: 

```{r}
ggplot(world_map2, aes(x=long,y=lat,group=group,fill=country)) + 
    geom_polygon(color="black",alpha=.8,linewidth=.1) + 
    scale_fill_manual(values=c("papayawhip","peachpuff2","peachpuff2","white","white","white","white","white","peachpuff2","firebrick4","peachpuff2","white","white","salmon3","peachpuff2","peachpuff2","white","white","white","white","peachpuff2","peachpuff2","peachpuff2","peachpuff2","peachpuff2","peachpuff2","white","white","white","peachpuff2","papayawhip","firebrick4","peachpuff2","peachpuff2","peachpuff2","white","peachpuff2","peachpuff2","lightsalmon1","white","peachpuff2","white","peachpuff2","white","white","salmon3","firebrick4","white","white","peachpuff2","white","papayawhip","white","white","peachpuff2","papayawhip","peachpuff2","white","white","peachpuff2","peachpuff2","peachpuff2","white","white","white","peachpuff2","lightsalmon1","peachpuff2","white","white","peachpuff2","white","peachpuff2","white","white","peachpuff2","peachpuff2","salmon3","white","white","white","white","papayawhip","peachpuff2","lightsalmon3","peachpuff2","peachpuff2","white","white","white","white","peachpuff2","white","white","white","peachpuff2","white","white","peachpuff2","peachpuff2","peachpuff2","peachpuff2","papayawhip","papayawhip","lightsalmon1","white","peachpuff2","white","peachpuff2","lightsalmon1","peachpuff2","lightsalmon1","white","peachpuff2","peachpuff2","peachpuff2","white","white","peachpuff2","peachpuff2","white","peachpuff2","peachpuff2","white","white","white","white","peachpuff2","peachpuff2","peachpuff2","papayawhip","white","peachpuff2","peachpuff2","peachpuff2","peachpuff2","peachpuff2","white","white","peachpuff2","peachpuff2","white","salmon3","white","papayawhip","white","white","peachpuff2","white","peachpuff2","white","white","papayawhip","white","peachpuff2","peachpuff2","white","peachpuff2","peachpuff2","peachpuff2","white","white","white","white","peachpuff2","white","peachpuff2","peachpuff2","peachpuff2","white","white","peachpuff2","white","lightsalmon1","peachpuff2","peachpuff2","white","peachpuff2","peachpuff2","white","white","white","peachpuff2","tomato4","papayawhip","white","white","white","white","white","white","white","papayawhip","peachpuff2","papayawhip","peachpuff2","white","white","white","white","white","white","peachpuff2","peachpuff2","white","white","peachpuff2","white","lightsalmon3","white","white","lightsalmon1","papayawhip","white","white","white","white","peachpuff2","peachpuff2","peachpuff2","white","peachpuff2","white","papayawhip","peachpuff2","white","papayawhip","white","white","peachpuff2","salmon4","white","white","papayawhip","peachpuff2","white","lightsalmon3","firebrick4","peachpuff2","white","papayawhip","white","lightsalmon3","white","white","white","white","papayawhip","papayawhip","papayawhip")) +
    xlab(" ") + 
    ylab(" ") + 
    guides(fill="none") +
    ggtitle("Figure 2. Choropleth map showing the mean anticipated country-level reductions in diet-attributable emissions for each of the 133 included countries.") +
    theme(panel.background=element_rect(fill="aliceblue"),panel.border=element_rect(fill=NA),axis.ticks=element_blank(),axis.text=element_blank(),panel.grid=element_blank())
```

## Trying out ggpattern

```{r}
pattern_map <- map_data("world")
```

```{r}
ggplot(world_map2, aes(map_id=country)) +
    geom_map_pattern(
      aes(
        pattern_fill    = "black",
        pattern_spacing = country,
        pattern_density = country,
        pattern_angle   = country,
        pattern         = country
      ),
      fill   = 'white',
      colour = 'black',
      pattern_aspect_ratio = 1.8,
      map    = pattern_map
    ) +
    expand_limits(x = pattern_map$long, y = pattern_map$lat) +
    coord_map() +
    theme_bw(18) +
    labs(title = "ggpattern::geom_map_pattern()") + 
    scale_pattern_density_discrete(range = c(0.01, 0.3)) + 
    scale_pattern_spacing_discrete(range = c(0.01, 0.03)) + 
    theme(legend.position = 'none')
```


