---
title: "figure-script"
output: github_document
date: "2023-02-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required Packages

```{r}
library(tidyverse)
library(dplyr)
```

## Data Loading

First, we load in the `world_map` data set included embedded within the ``ggplot2` package. We do this by assigning it as an object within our environment:

```{r}
world_map <- ggplot2::map_data("world")
```

From here, we need to update `ggplot2::map_data('world')` to be compatible with datasets using ISO country codes. We can accomplish this by using this tutorial provided by Haslam (2021): https://rpubs.com/Thom_JH/798825.

The essential components required for this project are outlined sequentially in the code chunks below.

```{r}
world_map2 <- world_map %>% 
  rename(country = region) %>%
  mutate(country = case_when(country == "Macedonia" ~ "North Macedonia" ,
  country == "Ivory Coast"  ~ "Cote d'Ivoire",
  country == "Democratic Republic of the Congo"  ~ "Congo, Dem. Rep.",
  country == "Republic of Congo" ~  "Congo, Rep.",
  country == "UK" ~  "United Kingdom",
  country == "USA" ~  "United States",
  country == "Laos" ~  "Lao",
  country == "Slovakia" ~  "Slovak Republic",
  country == "Saint Lucia" ~  "St. Lucia",
  country == "Kyrgyzstan"  ~  "Kyrgyz Republic",
  country == "Micronesia" ~ "Micronesia, Fed. Sts.",
  country == "Swaziland"  ~ "Eswatini", 
  country == "Virgin Islands"  ~ "Virgin Islands (U.S.)", 
  TRUE ~ country))
```

```{r}
match_names <- c("Antigua" , "Barbuda", "Nevis", "Saint Kitts", "Trinidad", "Tobago", "Grenadines", "Saint Vincent")
```

```{r}
map_match <- world_map2 %>% 
  filter(country %in% match_names)
```

```{r}
map_match %>% distinct(country)

ant_bar <- c(137 ,138 )

kit_nev <- c(930 , 931)

tri_tog <- c(1425, 1426)

vin_gre <- c(1575, 1576, 1577)
```

```{r}
new_names_ref <- c("Antigua and Barbuda", "St. Kitts and Nevis","Trinidad and Tobago", "St. Vincent and the Grenadines")
```

```{r}
map_match <- map_match %>% 
  mutate(country = case_when(group %in% ant_bar ~ "Antigua and Barbuda",group %in% kit_nev  ~ "St. Kitts and Nevis" ,group %in% tri_tog  ~ "Trinidad and Tobago" ,group %in% vin_gre ~ "St. Vincent and the Grenadines") ) %>% 
  tibble()
```

```{r}
map_match %>% head()

map_match %>% 
  distinct(country)%>% 
  knitr::kable(caption = "Add to World Map")

map_match %>% 
  group_by(country) %>% 
  count(group)  %>% 
  knitr::kable(caption = "Add to World Map")

map_match %>% 
  str()
```


```{r}
world_map2 %>% 
  str()

world_map2 <-  world_map2 %>%
  filter(!country %in% match_names)

world_map2 <- world_map2 %>% 
  bind_rows(map_match) %>%
  arrange(country)  %>%
  tibble()

world_map2 %>% 
  filter(country %in% match_names)

world_map2 %>% 
  filter(country %in% new_names_ref) %>%
  group_by(country) %>%
  slice_max(order, n = 1)
```

```{r}
sub_sleeps <- c("Hong Kong", "Macao")

hk_mc <- world_map2 %>% 
  filter(subregion %in% sub_sleeps)

hk_mc <- hk_mc %>%
  mutate(country = case_when(subregion == "Hong Kong" ~ "Hong Kong, China" ,
  subregion == "Macao" ~ "Macao, China" ))

hk_mc %>% 
  slice(38:41) %>% 
  knitr::kable(caption ="Check structure")
```

```{r}
world_map2 <-   world_map2 %>%
  filter(!subregion %in% sub_sleeps)

world_map2 <- world_map2 %>% 
  bind_rows(hk_mc) %>%
  select(-subregion) %>% 
  tibble()
```


