---
title: "Data Cleaning and Aggregation"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required Packages 

```{r, message=FALSE}
library(tidyverse)
```

## Loading in Our Shapefile Data

Before we can synthesize the relevant variables from our two identified data sources into a single matrix, we will need to first read in the nation-state shapefile data local to the `maps` package within `tidyverse`. 

```{r, message=TRUE}
map_data <- map_data("world") 
map_data %>%
  head(5)
```

Because the directory of nation-states used in this package does not adhere to the conventions laid out by the International Organization for Standardization (ISO), we will need to make a series of manual changes to better align our shapefile data with our university-enrollment and dietary-footprint data.

Using the instructions laid out by Thomas Haslam in his 2021 [*RPubs* entry](https://rpubs.com/Thom_JH/798825), we can begin by addressing what he refers to as the "easy cases."

In the mentioned [*RPubs* entry](https://rpubs.com/Thom_JH/798825) entry, Haslam identifies a total of 21 differences between the nation-states listed in the `maps` package and countries listed by [Gapminder](gapminder.org). 

The "easy cases," then, refer to the 13 instances where the names of the `regions` listed in the `maps` package and the countries listed by Gapminder are incongruent.

```{r}
map_data_iso <- map_data %>% 
  rename(country=region) %>%
  mutate(country=case_when(country=="Macedonia"~"North Macedonia",
                           country=="Ivory Coast"~"Cote d'Ivoire",
                           country=="Democratic Republic of the Congo"~"Congo, Dem. Rep.",
                           country=="Republic of Congo"~"Congo, Rep.",
                           country=="UK"~"United Kingdom",
                           country=="USA"~"United States",
                           country=="Laos"~"Lao",
                           country=="Slovakia"~"Slovak Republic",
                           country=="Saint Lucia"~"St. Lucia",
                           country=="Kyrgyzstan"~"Krygyz Republic",
                           country=="Micronesia"~"Micronesia, Fed. Sts.",
                           country=="Swaziland"~"Eswatini",
                           country=="Virgin Islands"~"Virgin Islands (U.S.)",
                        TRUE~country))
```

The second group of instances, which he refers to as the "island nations", refer to the 8 cases where discrete island `region` need to be aggregated to match the related `country` designations provided by [Gapminder](gapminder.org) and the ISO. 

```{r}
island_nations <- c("Antigua","Barbuda","Nevis", 
                 "Saint Kitts","Trinidad",
                 "Tobago","Grenadines","Saint Vincent")
island_nations_match <- map_data_iso %>% 
  filter(country %in% island_nations)
island_nations_match %>% distinct(country)
```

```{r}
ant_bar <- c(137,138 )
kit_nev <- c(930,931)
tri_tog <- c(1425,1426)
vin_gre <- c(1575,1576,1577)
island_nation_names <- c("Antigua and Barbuda","St. Kitts and Nevis","Trinidad and Tobago","St. Vincent and the Grenadines")
island_nations_match <- island_nations_match %>% 
  mutate(country=case_when(group %in% ant_bar~"Antigua and Barbuda",
                           group %in% kit_nev~"St. Kitts and Nevis",
                           group %in% tri_tog~"Trinidad and Tobago",
                           group %in% vin_gre~"St. Vincent and the Grenadines")) %>% 
  tibble()
```

```{r}
island_nations_match %>%
  distinct(country) 
```

```{r}
map_data_iso <- map_data_iso %>%
  filter(!country %in% island_nation_names)
map_data_iso <- map_data_iso %>% 
  bind_rows(island_nations_match) %>%
  arrange(country) %>%
  tibble()
```

Now, we move onto the final 2 cases that we will be addressing. Haslam refers to these as the instances of "subregion promotion". Here, we take Macao and Hong Kong, Special Administrative Regions of China designated as subregions in the `maps` package, and assign them as countries, as is convention for global studies research. 

```{r}
sra_names <- c("Hong Kong","Macao")
hk_mc <- map_data_iso %>% 
  filter(subregion %in% sra_names)
hk_mc <- hk_mc %>%
  mutate(country = case_when(subregion=="Hong Kong"~"Hong Kong, China",
                             subregion=="Macao"~"Macao, China"))
```

```{r}
map_data_iso <- map_data_iso %>%
  filter(!subregion %in% sra_names)
map_data_iso <- map_data_iso %>% 
  bind_rows(hk_mc) %>%
  select(-subregion) %>% 
  tibble()
```

With these each of these steps complete, the regions accounted for within our shapefile data are now as follows: 

```{r}
map_data_iso %>% distinct(country)
```

## Loading in Our Dietary Footprint Data

Before we can spatially join the relevant columns from our dietary footprint data with our updated shapefile data, we will need to first read in the corresponding file from the `parent-datasets` folder in our repository.

```{r}
dietary_footprint_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/dietary_footprint_data.csv")
dietary_footprint_data %>%
  head(6)
```

Because this dataset is not currently formatted in a way that aligns with the demands of our analysis, we will need to make several changes in preparation for our spatial join. 

For each country listed, we need to wrangle the baseline data such that there is a column corresponding to the quantities listed in the `value`, `centile_up`, and `centile_down` for each of the following attributes:`kg_co2e_excl_luc`, `kg_co2e_total`, `l_blue_wf_total`, `l_green_wf`, and `l_blue_green_wf`. In addition, this process needs to be repeated for each of the 8 remaining dietary conditions of interest: `2/3_vegan`, `baseline`, `lacto_ovo_vegetarian`, `low_red_meat`, `meatless_day`, `no_dairy`, `no_red_meat`, and `vegan`.

To adjust for these requirements, we will first select out the relevant variables.

```{r}
dietary_footprint_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/dietary_footprint_data.csv") %>%
  select(country,diet,attribute,value)
dietary_footprint_data %>%
  head(6)
```

With this accomplished, we will continue the wrangling process by pivoting to a wider format. We will achieve this by assigning the different dietary scenarios and attributes designated under the `diet` and `attribute` columns, respectively, as variables rather than observations.

```{r}
dietary_footprint_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/dietary_footprint_data.csv") %>%
  select(country,diet,attribute,value) %>%
  pivot_wider(names_from=c(diet,attribute),
              values_from="value")
dietary_footprint_data %>%
  head(6)
```

Finally, with these new variables generated we will, again, select out the combinations of dietary scenarios and attributes relevant to our analyses. 

```{r}
dietary_footprint_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/dietary_footprint_data.csv") %>%
  select(country,diet,attribute,value) %>%
  pivot_wider(names_from=c(diet,attribute),
              values_from="value") %>%
  select(country,
  "baseline_kg_co2e_excl_luc",
  "baseline_kg_co2e_total",
  "baseline_l_blue_green_wf",
  "baseline_l_blue_wf_total",
  "baseline_l_green_wf",
  "meatless_day_kg_co2e_excl_luc",
  "meatless_day_kg_co2e_total",
  "meatless_day_l_blue_green_wf",
  "meatless_day_l_blue_wf_total",
  "meatless_day_l_green_wf",
  "no_dairy_kg_co2e_excl_luc",
  "no_dairy_kg_co2e_total",
  "no_dairy_l_blue_green_wf",
  "no_dairy_l_blue_wf_total",
  "no_dairy_l_green_wf",
  "low_red_meat_kg_co2e_excl_luc",
  "low_red_meat_kg_co2e_total",
  "low_red_meat_l_blue_green_wf",
  "low_red_meat_l_blue_wf_total",
  "low_red_meat_l_green_wf",
  "no_red_meat_kg_co2e_excl_luc",
  "no_red_meat_kg_co2e_total",
  "no_red_meat_l_blue_green_wf",
  "no_red_meat_l_blue_wf_total",
  "no_red_meat_l_green_wf",
  "pescetarian_kg_co2e_excl_luc",
  "pescetarian_kg_co2e_total",
  "pescetarian_l_blue_green_wf",
  "pescetarian_l_blue_wf_total",
  "pescetarian_l_green_wf",
  "lacto_ovo_vegetarian_kg_co2e_excl_luc",
  "lacto_ovo_vegetarian_kg_co2e_total",
  "lacto_ovo_vegetarian_l_blue_green_wf",
  "lacto_ovo_vegetarian_l_blue_wf_total",
  "lacto_ovo_vegetarian_l_green_wf",
  "2/3_vegan_kg_co2e_excl_luc",
  "2/3_vegan_kg_co2e_total",
  "2/3_vegan_l_blue_green_wf",
  "2/3_vegan_l_blue_wf_total",
  "2/3_vegan_l_green_wf",
  "vegan_kg_co2e_excl_luc",
  "vegan_kg_co2e_total",
  "vegan_l_blue_green_wf",
  "vegan_l_blue_wf_total",
  "vegan_l_green_wf")
dietary_footprint_data %>%
  head(6)
```

Finally, we will need to perform the necessary checks to ensure that country names are consistent across the data sources used for our map and dietary footprint variables.

We will also eventually need to use the `mutate` function to generate averages across scenarios.

## Spatially Joining Our Dietary Footprint Data

map gap

## Loading in Our University Enrollment Data

As we did for our dietary footprint data, we will need to read in and wrangle the university enrollment data found in the `parent-datasets` folder of our repository.

```{r}
university_enrollment_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/university_enrollment_data.csv") %>%
  as_tibble()
university_enrollment_data %>%
  head(6)
```

Before we can spatially join the relevant variables from this data source, we will need to make it so that the data associated with each included country is captured in a single row, and each subsequent column captures the following: (1) the total number of students enrolled in ISCED 6 programs, (2) the total number of students enrolled in ISCED 7 programs, (3) the total number of students enrolled in ISCED 8 programs, (4) the total number of people living within the country, and (5) the reference year being used for each of these variables.

We will begin this process by selecting out the `Country.Code` and `Series.Code` columns, slicing out the 5 bottommost rows, and renaming the `Country.Name`, `Series`, and reference year variables.

```{r}
university_enrollment_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/university_enrollment_data.csv") %>%
  select(-Country.Code,-Series.Code) %>%
  as_tibble(university_enrollment_data) %>%
  slice(1:(n()-5)) %>%
  rename(country=Country.Name,series=Series,yr2000=YR2000,yr2001=YR2001,yr2002=YR2002,yr2003=YR2003,yr2004=YR2004,yr2005=YR2005,yr2006=YR2006,yr2007=YR2007,yr2008=YR2008,yr2009=YR2009,yr2010=YR2010,yr2011=YR2011,yr2012=YR2012,yr2013=YR2013,yr2014=YR2014,yr2015=YR2015,yr2016=YR2016,yr2017=YR2017,yr2018=YR2018,yr2019=YR2019,yr2020=YR2020) 
university_enrollment_data %>%
  tail(6)
```

With this complete, we now need to convert the reference year columns from character strings (`chr`) to double strings (`dbl`), which will coincidently convert the default `--` entries to `NA` values.

```{r}
university_enrollment_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/university_enrollment_data.csv") %>%
  select(-Country.Code,-Series.Code) %>%
  as_tibble(university_enrollment_data) %>%
  slice(1:(n()-5)) %>%
  rename(country=Country.Name,series=Series,yr2000=YR2000,yr2001=YR2001,yr2002=YR2002,yr2003=YR2003,yr2004=YR2004,yr2005=YR2005,yr2006=YR2006,yr2007=YR2007,yr2008=YR2008,yr2009=YR2009,yr2010=YR2010,yr2011=YR2011,yr2012=YR2012,yr2013=YR2013,yr2014=YR2014,yr2015=YR2015,yr2016=YR2016,yr2017=YR2017,yr2018=YR2018,yr2019=YR2019,yr2020=YR2020) %>%
  mutate_at(c("yr2000","yr2001","yr2002","yr2003","yr2004","yr2005","yr2006","yr2007","yr2008","yr2009","yr2010","yr2011","yr2012","yr2013","yr2014","yr2015","yr2016","yr2017","yr2018","yr2019","yr2020"),as.double)
university_enrollment_data %>%
  head(6)
```

We will now turn all of the NA variables in the reference year columns from `NA` values to zero in order to more easily set up our conditional rules for pulling the most recent year with recorded data.

```{r}
university_enrollment_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/university_enrollment_data.csv") %>%
  select(-Country.Code,-Series.Code) %>%
  as_tibble(university_enrollment_data) %>%
  slice(1:(n()-5)) %>%
  rename(country=Country.Name,series=Series,yr2000=YR2000,yr2001=YR2001,yr2002=YR2002,yr2003=YR2003,yr2004=YR2004,yr2005=YR2005,yr2006=YR2006,yr2007=YR2007,yr2008=YR2008,yr2009=YR2009,yr2010=YR2010,yr2011=YR2011,yr2012=YR2012,yr2013=YR2013,yr2014=YR2014,yr2015=YR2015,yr2016=YR2016,yr2017=YR2017,yr2018=YR2018,yr2019=YR2019,yr2020=YR2020) %>%
  mutate_at(c("yr2000","yr2001","yr2002","yr2003","yr2004","yr2005","yr2006","yr2007","yr2008","yr2009","yr2010","yr2011","yr2012","yr2013","yr2014","yr2015","yr2016","yr2017","yr2018","yr2019","yr2020"),as.double) %>%
  replace(is.na(.),0)
university_enrollment_data %>%
  head(6)
```

Now, we will pivot our dataframe so that the different variables of interest currently captured in the `series` column are instead represented as their own variables. Because the new column names will be a function of how our four observations are named, we will also add the necessary code to shorten these descriptions.

```{r}
university_enrollment_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/university_enrollment_data.csv") %>%
  select(-Country.Code,-Series.Code) %>%
  as_tibble(university_enrollment_data) %>%
  slice(1:(n()-5)) %>%
  rename(country=Country.Name,series=Series,yr2000=YR2000,yr2001=YR2001,yr2002=YR2002,yr2003=YR2003,yr2004=YR2004,yr2005=YR2005,yr2006=YR2006,yr2007=YR2007,yr2008=YR2008,yr2009=YR2009,yr2010=YR2010,yr2011=YR2011,yr2012=YR2012,yr2013=YR2013,yr2014=YR2014,yr2015=YR2015,yr2016=YR2016,yr2017=YR2017,yr2018=YR2018,yr2019=YR2019,yr2020=YR2020) %>%
  mutate_at(c("yr2000","yr2001","yr2002","yr2003","yr2004","yr2005","yr2006","yr2007","yr2008","yr2009","yr2010","yr2011","yr2012","yr2013","yr2014","yr2015","yr2016","yr2017","yr2018","yr2019","yr2020"),as.double) %>%
  replace(is.na(.),0) %>%
  distinct() %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 6 programmes, both sexes (number)"),"isced6_enr")) %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 7 programmes, both sexes (number)"),"isced7_enr")) %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 8 programmes, both sexes (number)"),"isced8_enr")) %>%
  mutate(across("series",str_replace, fixed("Population, total"),"nat_pop")) %>%
  pivot_wider(names_from="series",
              values_from=c("yr2020","yr2019","yr2018","yr2017","yr2016","yr2015","yr2014","yr2013","yr2012","yr2011","yr2010","yr2009","yr2008","yr2007","yr2006","yr2005","yr2004","yr2003","yr2002","yr2001","yr2000"))
university_enrollment_data %>%
  head(6)
```

We are now left with a format that is closer to our desired specifications, where the data associated with each included country corresponds to one row, with concatenated column titles representing a population total and the reference year being used.
  
For each country, we want to use the most recent year that there is recorded data for both our national population variable (which is collected more consistently) and each of our stratified ISCED enrollment population variables (which are collected less consistently).

The challenge now is to find a way to conditionally mutate five new columns: (1) one that captures the number of people living with the country, (2) one that captures the number of people in that country enrolled in ISCED 6 programs, (3) one that captures the number of people in that country enrolled in ISCED 7 programs, (4) one that captures the number of people in that country enrolled in ISCED 8 programs, and, finally, (5) another that notes the reference year being used across the four constructed variables.

For this last variable, we will need to first create a column for the number of ISCED 6, ISCED 7, and ISCED 8 enrollees, as well as for the national population variable, to evaluate how to coalesce onto the same reference year.

```{r}
university_enrollment_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/university_enrollment_data.csv") %>%
  select(-Country.Code,-Series.Code) %>%
  as_tibble(university_enrollment_data) %>%
  slice(1:(n()-5)) %>%
  rename(country=Country.Name,series=Series,yr2000=YR2000,yr2001=YR2001,yr2002=YR2002,yr2003=YR2003,yr2004=YR2004,yr2005=YR2005,yr2006=YR2006,yr2007=YR2007,yr2008=YR2008,yr2009=YR2009,yr2010=YR2010,yr2011=YR2011,yr2012=YR2012,yr2013=YR2013,yr2014=YR2014,yr2015=YR2015,yr2016=YR2016,yr2017=YR2017,yr2018=YR2018,yr2019=YR2019,yr2020=YR2020) %>%
  mutate_at(c("yr2000","yr2001","yr2002","yr2003","yr2004","yr2005","yr2006","yr2007","yr2008","yr2009","yr2010","yr2011","yr2012","yr2013","yr2014","yr2015","yr2016","yr2017","yr2018","yr2019","yr2020"),as.double) %>%
  replace(is.na(.),0) %>%
  distinct() %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 6 programmes, both sexes (number)"),"isced6_enr")) %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 7 programmes, both sexes (number)"),"isced7_enr")) %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 8 programmes, both sexes (number)"),"isced8_enr")) %>%
  mutate(across("series",str_replace, fixed("Population, total"),"nat_pop")) %>%
  pivot_wider(names_from="series",
              values_from=c("yr2020","yr2019","yr2018","yr2017","yr2016","yr2015","yr2014","yr2013","yr2012","yr2011","yr2010","yr2009","yr2008","yr2007","yr2006","yr2005","yr2004","yr2003","yr2002","yr2001","yr2000")) %>%
  mutate(isced6_ref_year=ifelse(yr2020_isced6_enr>0,2020,ifelse(yr2019_isced6_enr>0,2019,ifelse(yr2018_isced6_enr>0,2018,ifelse(yr2017_isced6_enr>0,2017,ifelse(yr2016_isced6_enr>0,2016,ifelse(yr2015_isced6_enr>0,2015,ifelse(yr2014_isced6_enr>0,2014,ifelse(yr2013_isced6_enr>0,2013,ifelse(yr2012_isced6_enr>0,2012,ifelse(yr2011_isced6_enr>0,2011,ifelse(yr2010_isced6_enr>0,2010,ifelse(yr2009_isced6_enr>0,2009,ifelse(yr2008_isced6_enr>0,2008,ifelse(yr2007_isced6_enr>0,2007,ifelse(yr2006_isced6_enr>0,2006,ifelse(yr2005_isced6_enr>0,2005,ifelse(yr2004_isced6_enr>0,2004,ifelse(yr2003_isced6_enr>0,2003,ifelse(yr2002_isced6_enr>0,2002,ifelse(yr2001_isced6_enr>0,2001,ifelse(yr2000_isced6_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(isced7_ref_yr=ifelse(yr2020_isced7_enr>0,2020,ifelse(yr2019_isced7_enr>0,2019,ifelse(yr2018_isced7_enr>0,2018,ifelse(yr2017_isced7_enr>0,2017,ifelse(yr2016_isced7_enr>0,2016,ifelse(yr2015_isced7_enr>0,2015,ifelse(yr2014_isced7_enr>0,2014,ifelse(yr2013_isced7_enr>0,2013,ifelse(yr2012_isced7_enr>0,2012,ifelse(yr2011_isced7_enr>0,2011,ifelse(yr2010_isced7_enr>0,2010,ifelse(yr2009_isced7_enr>0,2009,ifelse(yr2008_isced7_enr>0,2008,ifelse(yr2007_isced7_enr>0,2007,ifelse(yr2006_isced7_enr>0,2006,ifelse(yr2005_isced7_enr>0,2005,ifelse(yr2004_isced7_enr>0,2004,ifelse(yr2003_isced7_enr>0,2003,ifelse(yr2002_isced7_enr>0,2002,ifelse(yr2001_isced7_enr>0,2001,ifelse(yr2000_isced7_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(isced8_ref_yr=ifelse(yr2020_isced8_enr>0,2020,ifelse(yr2019_isced8_enr>0,2019,ifelse(yr2018_isced8_enr>0,2018,ifelse(yr2017_isced8_enr>0,2017,ifelse(yr2016_isced8_enr>0,2016,ifelse(yr2015_isced8_enr>0,2015,ifelse(yr2014_isced8_enr>0,2014,ifelse(yr2013_isced8_enr>0,2013,ifelse(yr2012_isced8_enr>0,2012,ifelse(yr2011_isced8_enr>0,2011,ifelse(yr2010_isced8_enr>0,2010,ifelse(yr2009_isced8_enr>0,2009,ifelse(yr2008_isced8_enr>0,2008,ifelse(yr2007_isced8_enr>0,2007,ifelse(yr2006_isced8_enr>0,2006,ifelse(yr2005_isced8_enr>0,2005,ifelse(yr2004_isced8_enr>0,2004,ifelse(yr2003_isced8_enr>0,2003,ifelse(yr2002_isced8_enr>0,2002,ifelse(yr2001_isced8_enr>0,2001,ifelse(yr2000_isced8_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(natpop_ref_yr=ifelse(yr2020_nat_pop>0,2020,ifelse(yr2019_nat_pop>0,2019,ifelse(yr2018_nat_pop>0,2018,ifelse(yr2017_nat_pop>0,2017,ifelse(yr2016_nat_pop>0,2016,ifelse(yr2015_nat_pop>0,2015,ifelse(yr2014_nat_pop>0,2014,ifelse(yr2013_nat_pop>0,2013,ifelse(yr2012_nat_pop>0,2012,ifelse(yr2011_nat_pop>0,2011,ifelse(yr2010_nat_pop>0,2010,ifelse(yr2009_nat_pop>0,2009,ifelse(yr2008_nat_pop>0,2008,ifelse(yr2007_nat_pop>0,2007,ifelse(yr2006_nat_pop>0,2006,ifelse(yr2005_nat_pop>0,2005,ifelse(yr2004_nat_pop>0,2004,ifelse(yr2003_nat_pop>0,2003,ifelse(yr2002_nat_pop>0,2002,ifelse(yr2001_nat_pop>0,2001,ifelse(yr2000_nat_pop>0,2000,0))))))))))))))))))))))
university_enrollment_data %>%
  head(6)
```

From a quick glance, we can see that for the countries with available data across multiple VOIs, that there are inconsistencies in when the most recent year with recorded data was. Therefore, the assumption that the collection of these ISCED enrollee estimatesoccur at the same intervals, and thus would have the same reference year, has been violated.

While we figure out the best solution for dealing with this, we do know that for the countries that have `0` values across the newly generated `isced6_ref_yr`, `isced7_ref_yr`, and `isced8_ref_yr` columns can be removed, given that they do not have data available for university enrollment.

Here, we list the countries that meet this condition, whereby the sum of `isced6_ref_yr`, `isced7_ref_yr`, and `isced8_ref_yr` is equivalent to `0`.

```{r}
university_enrollment_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/university_enrollment_data.csv") %>%
  select(-Country.Code,-Series.Code) %>%
  as_tibble(university_enrollment_data) %>%
  slice(1:(n()-5)) %>%
  rename(country=Country.Name,series=Series,yr2000=YR2000,yr2001=YR2001,yr2002=YR2002,yr2003=YR2003,yr2004=YR2004,yr2005=YR2005,yr2006=YR2006,yr2007=YR2007,yr2008=YR2008,yr2009=YR2009,yr2010=YR2010,yr2011=YR2011,yr2012=YR2012,yr2013=YR2013,yr2014=YR2014,yr2015=YR2015,yr2016=YR2016,yr2017=YR2017,yr2018=YR2018,yr2019=YR2019,yr2020=YR2020) %>%
  mutate_at(c("yr2000","yr2001","yr2002","yr2003","yr2004","yr2005","yr2006","yr2007","yr2008","yr2009","yr2010","yr2011","yr2012","yr2013","yr2014","yr2015","yr2016","yr2017","yr2018","yr2019","yr2020"),as.double) %>%
  replace(is.na(.),0) %>%
  distinct() %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 6 programmes, both sexes (number)"),"isced6_enr")) %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 7 programmes, both sexes (number)"),"isced7_enr")) %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 8 programmes, both sexes (number)"),"isced8_enr")) %>%
  mutate(across("series",str_replace, fixed("Population, total"),"nat_pop")) %>%
  pivot_wider(names_from="series",
              values_from=c("yr2020","yr2019","yr2018","yr2017","yr2016","yr2015","yr2014","yr2013","yr2012","yr2011","yr2010","yr2009","yr2008","yr2007","yr2006","yr2005","yr2004","yr2003","yr2002","yr2001","yr2000")) %>%
  mutate(isced6_ref_yr=ifelse(yr2020_isced6_enr>0,2020,ifelse(yr2019_isced6_enr>0,2019,ifelse(yr2018_isced6_enr>0,2018,ifelse(yr2017_isced6_enr>0,2017,ifelse(yr2016_isced6_enr>0,2016,ifelse(yr2015_isced6_enr>0,2015,ifelse(yr2014_isced6_enr>0,2014,ifelse(yr2013_isced6_enr>0,2013,ifelse(yr2012_isced6_enr>0,2012,ifelse(yr2011_isced6_enr>0,2011,ifelse(yr2010_isced6_enr>0,2010,ifelse(yr2009_isced6_enr>0,2009,ifelse(yr2008_isced6_enr>0,2008,ifelse(yr2007_isced6_enr>0,2007,ifelse(yr2006_isced6_enr>0,2006,ifelse(yr2005_isced6_enr>0,2005,ifelse(yr2004_isced6_enr>0,2004,ifelse(yr2003_isced6_enr>0,2003,ifelse(yr2002_isced6_enr>0,2002,ifelse(yr2001_isced6_enr>0,2001,ifelse(yr2000_isced6_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(isced7_ref_yr=ifelse(yr2020_isced7_enr>0,2020,ifelse(yr2019_isced7_enr>0,2019,ifelse(yr2018_isced7_enr>0,2018,ifelse(yr2017_isced7_enr>0,2017,ifelse(yr2016_isced7_enr>0,2016,ifelse(yr2015_isced7_enr>0,2015,ifelse(yr2014_isced7_enr>0,2014,ifelse(yr2013_isced7_enr>0,2013,ifelse(yr2012_isced7_enr>0,2012,ifelse(yr2011_isced7_enr>0,2011,ifelse(yr2010_isced7_enr>0,2010,ifelse(yr2009_isced7_enr>0,2009,ifelse(yr2008_isced7_enr>0,2008,ifelse(yr2007_isced7_enr>0,2007,ifelse(yr2006_isced7_enr>0,2006,ifelse(yr2005_isced7_enr>0,2005,ifelse(yr2004_isced7_enr>0,2004,ifelse(yr2003_isced7_enr>0,2003,ifelse(yr2002_isced7_enr>0,2002,ifelse(yr2001_isced7_enr>0,2001,ifelse(yr2000_isced7_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(isced8_ref_yr=ifelse(yr2020_isced8_enr>0,2020,ifelse(yr2019_isced8_enr>0,2019,ifelse(yr2018_isced8_enr>0,2018,ifelse(yr2017_isced8_enr>0,2017,ifelse(yr2016_isced8_enr>0,2016,ifelse(yr2015_isced8_enr>0,2015,ifelse(yr2014_isced8_enr>0,2014,ifelse(yr2013_isced8_enr>0,2013,ifelse(yr2012_isced8_enr>0,2012,ifelse(yr2011_isced8_enr>0,2011,ifelse(yr2010_isced8_enr>0,2010,ifelse(yr2009_isced8_enr>0,2009,ifelse(yr2008_isced8_enr>0,2008,ifelse(yr2007_isced8_enr>0,2007,ifelse(yr2006_isced8_enr>0,2006,ifelse(yr2005_isced8_enr>0,2005,ifelse(yr2004_isced8_enr>0,2004,ifelse(yr2003_isced8_enr>0,2003,ifelse(yr2002_isced8_enr>0,2002,ifelse(yr2001_isced8_enr>0,2001,ifelse(yr2000_isced8_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(natpop_ref_yr=ifelse(yr2020_nat_pop>0,2020,ifelse(yr2019_nat_pop>0,2019,ifelse(yr2018_nat_pop>0,2018,ifelse(yr2017_nat_pop>0,2017,ifelse(yr2016_nat_pop>0,2016,ifelse(yr2015_nat_pop>0,2015,ifelse(yr2014_nat_pop>0,2014,ifelse(yr2013_nat_pop>0,2013,ifelse(yr2012_nat_pop>0,2012,ifelse(yr2011_nat_pop>0,2011,ifelse(yr2010_nat_pop>0,2010,ifelse(yr2009_nat_pop>0,2009,ifelse(yr2008_nat_pop>0,2008,ifelse(yr2007_nat_pop>0,2007,ifelse(yr2006_nat_pop>0,2006,ifelse(yr2005_nat_pop>0,2005,ifelse(yr2004_nat_pop>0,2004,ifelse(yr2003_nat_pop>0,2003,ifelse(yr2002_nat_pop>0,2002,ifelse(yr2001_nat_pop>0,2001,ifelse(yr2000_nat_pop>0,2000,0)))))))))))))))))))))) %>%
  filter(isced6_ref_yr+isced7_ref_yr+isced8_ref_yr==0)
university_enrollment_data %>%
  select(country,isced6_ref_yr,isced7_ref_yr,isced8_ref_yr) 
```

Now, we remove those rows from the dataframe here:

```{r}
university_enrollment_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/university_enrollment_data.csv") %>%
  select(-Country.Code,-Series.Code) %>%
  as_tibble(university_enrollment_data) %>%
  slice(1:(n()-5)) %>%
  rename(country=Country.Name,series=Series,yr2000=YR2000,yr2001=YR2001,yr2002=YR2002,yr2003=YR2003,yr2004=YR2004,yr2005=YR2005,yr2006=YR2006,yr2007=YR2007,yr2008=YR2008,yr2009=YR2009,yr2010=YR2010,yr2011=YR2011,yr2012=YR2012,yr2013=YR2013,yr2014=YR2014,yr2015=YR2015,yr2016=YR2016,yr2017=YR2017,yr2018=YR2018,yr2019=YR2019,yr2020=YR2020) %>%
  mutate_at(c("yr2000","yr2001","yr2002","yr2003","yr2004","yr2005","yr2006","yr2007","yr2008","yr2009","yr2010","yr2011","yr2012","yr2013","yr2014","yr2015","yr2016","yr2017","yr2018","yr2019","yr2020"),as.double) %>%
  replace(is.na(.),0) %>%
  distinct() %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 6 programmes, both sexes (number)"),"isced6_enr")) %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 7 programmes, both sexes (number)"),"isced7_enr")) %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 8 programmes, both sexes (number)"),"isced8_enr")) %>%
  mutate(across("series",str_replace, fixed("Population, total"),"nat_pop")) %>%
  pivot_wider(names_from="series",
              values_from=c("yr2020","yr2019","yr2018","yr2017","yr2016","yr2015","yr2014","yr2013","yr2012","yr2011","yr2010","yr2009","yr2008","yr2007","yr2006","yr2005","yr2004","yr2003","yr2002","yr2001","yr2000")) %>%
  mutate(isced6_ref_yr=ifelse(yr2020_isced6_enr>0,2020,ifelse(yr2019_isced6_enr>0,2019,ifelse(yr2018_isced6_enr>0,2018,ifelse(yr2017_isced6_enr>0,2017,ifelse(yr2016_isced6_enr>0,2016,ifelse(yr2015_isced6_enr>0,2015,ifelse(yr2014_isced6_enr>0,2014,ifelse(yr2013_isced6_enr>0,2013,ifelse(yr2012_isced6_enr>0,2012,ifelse(yr2011_isced6_enr>0,2011,ifelse(yr2010_isced6_enr>0,2010,ifelse(yr2009_isced6_enr>0,2009,ifelse(yr2008_isced6_enr>0,2008,ifelse(yr2007_isced6_enr>0,2007,ifelse(yr2006_isced6_enr>0,2006,ifelse(yr2005_isced6_enr>0,2005,ifelse(yr2004_isced6_enr>0,2004,ifelse(yr2003_isced6_enr>0,2003,ifelse(yr2002_isced6_enr>0,2002,ifelse(yr2001_isced6_enr>0,2001,ifelse(yr2000_isced6_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(isced7_ref_yr=ifelse(yr2020_isced7_enr>0,2020,ifelse(yr2019_isced7_enr>0,2019,ifelse(yr2018_isced7_enr>0,2018,ifelse(yr2017_isced7_enr>0,2017,ifelse(yr2016_isced7_enr>0,2016,ifelse(yr2015_isced7_enr>0,2015,ifelse(yr2014_isced7_enr>0,2014,ifelse(yr2013_isced7_enr>0,2013,ifelse(yr2012_isced7_enr>0,2012,ifelse(yr2011_isced7_enr>0,2011,ifelse(yr2010_isced7_enr>0,2010,ifelse(yr2009_isced7_enr>0,2009,ifelse(yr2008_isced7_enr>0,2008,ifelse(yr2007_isced7_enr>0,2007,ifelse(yr2006_isced7_enr>0,2006,ifelse(yr2005_isced7_enr>0,2005,ifelse(yr2004_isced7_enr>0,2004,ifelse(yr2003_isced7_enr>0,2003,ifelse(yr2002_isced7_enr>0,2002,ifelse(yr2001_isced7_enr>0,2001,ifelse(yr2000_isced7_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(isced8_ref_yr=ifelse(yr2020_isced8_enr>0,2020,ifelse(yr2019_isced8_enr>0,2019,ifelse(yr2018_isced8_enr>0,2018,ifelse(yr2017_isced8_enr>0,2017,ifelse(yr2016_isced8_enr>0,2016,ifelse(yr2015_isced8_enr>0,2015,ifelse(yr2014_isced8_enr>0,2014,ifelse(yr2013_isced8_enr>0,2013,ifelse(yr2012_isced8_enr>0,2012,ifelse(yr2011_isced8_enr>0,2011,ifelse(yr2010_isced8_enr>0,2010,ifelse(yr2009_isced8_enr>0,2009,ifelse(yr2008_isced8_enr>0,2008,ifelse(yr2007_isced8_enr>0,2007,ifelse(yr2006_isced8_enr>0,2006,ifelse(yr2005_isced8_enr>0,2005,ifelse(yr2004_isced8_enr>0,2004,ifelse(yr2003_isced8_enr>0,2003,ifelse(yr2002_isced8_enr>0,2002,ifelse(yr2001_isced8_enr>0,2001,ifelse(yr2000_isced8_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(natpop_ref_yr=ifelse(yr2020_nat_pop>0,2020,ifelse(yr2019_nat_pop>0,2019,ifelse(yr2018_nat_pop>0,2018,ifelse(yr2017_nat_pop>0,2017,ifelse(yr2016_nat_pop>0,2016,ifelse(yr2015_nat_pop>0,2015,ifelse(yr2014_nat_pop>0,2014,ifelse(yr2013_nat_pop>0,2013,ifelse(yr2012_nat_pop>0,2012,ifelse(yr2011_nat_pop>0,2011,ifelse(yr2010_nat_pop>0,2010,ifelse(yr2009_nat_pop>0,2009,ifelse(yr2008_nat_pop>0,2008,ifelse(yr2007_nat_pop>0,2007,ifelse(yr2006_nat_pop>0,2006,ifelse(yr2005_nat_pop>0,2005,ifelse(yr2004_nat_pop>0,2004,ifelse(yr2003_nat_pop>0,2003,ifelse(yr2002_nat_pop>0,2002,ifelse(yr2001_nat_pop>0,2001,ifelse(yr2000_nat_pop>0,2000,0)))))))))))))))))))))) %>%
  rowwise() %>%
  filter(!isced6_ref_yr+isced7_ref_yr+isced8_ref_yr==0) 
university_enrollment_data %>%
  head(6)
```

With these rows removed from the dataset, we can now move on to constructing the corresponding columns that pull the actual values, both for the national population variable as well as for the ISCED 6, 7, and 8 enrollee estimates.

```{r}
university_enrollment_data <- read.csv("/Users/kenjinchang/github/university-dining-impact-model/parent-datasets/university_enrollment_data.csv") %>%
  select(-Country.Code,-Series.Code) %>%
  as_tibble(university_enrollment_data) %>%
  slice(1:(n()-5)) %>%
  rename(country=Country.Name,series=Series,yr2000=YR2000,yr2001=YR2001,yr2002=YR2002,yr2003=YR2003,yr2004=YR2004,yr2005=YR2005,yr2006=YR2006,yr2007=YR2007,yr2008=YR2008,yr2009=YR2009,yr2010=YR2010,yr2011=YR2011,yr2012=YR2012,yr2013=YR2013,yr2014=YR2014,yr2015=YR2015,yr2016=YR2016,yr2017=YR2017,yr2018=YR2018,yr2019=YR2019,yr2020=YR2020) %>%
  mutate_at(c("yr2000","yr2001","yr2002","yr2003","yr2004","yr2005","yr2006","yr2007","yr2008","yr2009","yr2010","yr2011","yr2012","yr2013","yr2014","yr2015","yr2016","yr2017","yr2018","yr2019","yr2020"),as.double) %>%
  replace(is.na(.),0) %>%
  distinct() %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 6 programmes, both sexes (number)"),"isced6_enr")) %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 7 programmes, both sexes (number)"),"isced7_enr")) %>%
  mutate(across("series",str_replace, fixed("Enrolment in tertiary education, ISCED 8 programmes, both sexes (number)"),"isced8_enr")) %>%
  mutate(across("series",str_replace, fixed("Population, total"),"nat_pop")) %>%
  pivot_wider(names_from="series",
              values_from=c("yr2020","yr2019","yr2018","yr2017","yr2016","yr2015","yr2014","yr2013","yr2012","yr2011","yr2010","yr2009","yr2008","yr2007","yr2006","yr2005","yr2004","yr2003","yr2002","yr2001","yr2000")) %>%
  mutate(isced6_ref_yr=ifelse(yr2020_isced6_enr>0,2020,ifelse(yr2019_isced6_enr>0,2019,ifelse(yr2018_isced6_enr>0,2018,ifelse(yr2017_isced6_enr>0,2017,ifelse(yr2016_isced6_enr>0,2016,ifelse(yr2015_isced6_enr>0,2015,ifelse(yr2014_isced6_enr>0,2014,ifelse(yr2013_isced6_enr>0,2013,ifelse(yr2012_isced6_enr>0,2012,ifelse(yr2011_isced6_enr>0,2011,ifelse(yr2010_isced6_enr>0,2010,ifelse(yr2009_isced6_enr>0,2009,ifelse(yr2008_isced6_enr>0,2008,ifelse(yr2007_isced6_enr>0,2007,ifelse(yr2006_isced6_enr>0,2006,ifelse(yr2005_isced6_enr>0,2005,ifelse(yr2004_isced6_enr>0,2004,ifelse(yr2003_isced6_enr>0,2003,ifelse(yr2002_isced6_enr>0,2002,ifelse(yr2001_isced6_enr>0,2001,ifelse(yr2000_isced6_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(isced7_ref_yr=ifelse(yr2020_isced7_enr>0,2020,ifelse(yr2019_isced7_enr>0,2019,ifelse(yr2018_isced7_enr>0,2018,ifelse(yr2017_isced7_enr>0,2017,ifelse(yr2016_isced7_enr>0,2016,ifelse(yr2015_isced7_enr>0,2015,ifelse(yr2014_isced7_enr>0,2014,ifelse(yr2013_isced7_enr>0,2013,ifelse(yr2012_isced7_enr>0,2012,ifelse(yr2011_isced7_enr>0,2011,ifelse(yr2010_isced7_enr>0,2010,ifelse(yr2009_isced7_enr>0,2009,ifelse(yr2008_isced7_enr>0,2008,ifelse(yr2007_isced7_enr>0,2007,ifelse(yr2006_isced7_enr>0,2006,ifelse(yr2005_isced7_enr>0,2005,ifelse(yr2004_isced7_enr>0,2004,ifelse(yr2003_isced7_enr>0,2003,ifelse(yr2002_isced7_enr>0,2002,ifelse(yr2001_isced7_enr>0,2001,ifelse(yr2000_isced7_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(isced8_ref_yr=ifelse(yr2020_isced8_enr>0,2020,ifelse(yr2019_isced8_enr>0,2019,ifelse(yr2018_isced8_enr>0,2018,ifelse(yr2017_isced8_enr>0,2017,ifelse(yr2016_isced8_enr>0,2016,ifelse(yr2015_isced8_enr>0,2015,ifelse(yr2014_isced8_enr>0,2014,ifelse(yr2013_isced8_enr>0,2013,ifelse(yr2012_isced8_enr>0,2012,ifelse(yr2011_isced8_enr>0,2011,ifelse(yr2010_isced8_enr>0,2010,ifelse(yr2009_isced8_enr>0,2009,ifelse(yr2008_isced8_enr>0,2008,ifelse(yr2007_isced8_enr>0,2007,ifelse(yr2006_isced8_enr>0,2006,ifelse(yr2005_isced8_enr>0,2005,ifelse(yr2004_isced8_enr>0,2004,ifelse(yr2003_isced8_enr>0,2003,ifelse(yr2002_isced8_enr>0,2002,ifelse(yr2001_isced8_enr>0,2001,ifelse(yr2000_isced8_enr>0,2000,0)))))))))))))))))))))) %>%
  mutate(natpop_ref_yr=ifelse(yr2020_nat_pop>0,2020,ifelse(yr2019_nat_pop>0,2019,ifelse(yr2018_nat_pop>0,2018,ifelse(yr2017_nat_pop>0,2017,ifelse(yr2016_nat_pop>0,2016,ifelse(yr2015_nat_pop>0,2015,ifelse(yr2014_nat_pop>0,2014,ifelse(yr2013_nat_pop>0,2013,ifelse(yr2012_nat_pop>0,2012,ifelse(yr2011_nat_pop>0,2011,ifelse(yr2010_nat_pop>0,2010,ifelse(yr2009_nat_pop>0,2009,ifelse(yr2008_nat_pop>0,2008,ifelse(yr2007_nat_pop>0,2007,ifelse(yr2006_nat_pop>0,2006,ifelse(yr2005_nat_pop>0,2005,ifelse(yr2004_nat_pop>0,2004,ifelse(yr2003_nat_pop>0,2003,ifelse(yr2002_nat_pop>0,2002,ifelse(yr2001_nat_pop>0,2001,ifelse(yr2000_nat_pop>0,2000,0)))))))))))))))))))))) %>%
  mutate(isced6_enr=ifelse(yr2020_isced6_enr>0,yr2020_isced6_enr,ifelse(yr2019_isced6_enr>0,yr2019_isced6_enr,ifelse(yr2018_isced6_enr>0,yr2018_isced6_enr,ifelse(yr2017_isced6_enr>0,yr2017_isced6_enr,ifelse(yr2016_isced6_enr>0,yr2016_isced6_enr,ifelse(yr2015_isced6_enr>0,yr2015_isced6_enr,ifelse(yr2014_isced6_enr>0,yr2014_isced6_enr,ifelse(yr2013_isced6_enr>0,yr2013_isced6_enr,ifelse(yr2012_isced6_enr>0,yr2012_isced6_enr,ifelse(yr2011_isced6_enr>0,yr2011_isced6_enr,ifelse(yr2010_isced6_enr>0,yr2010_isced6_enr,ifelse(yr2009_isced6_enr>0,yr2009_isced6_enr,ifelse(yr2008_isced6_enr>0,yr2008_isced6_enr,ifelse(yr2007_isced6_enr>0,yr2007_isced6_enr,ifelse(yr2006_isced6_enr>0,yr2006_isced6_enr,ifelse(yr2005_isced6_enr>0,yr2005_isced6_enr,ifelse(yr2004_isced6_enr>0,yr2004_isced6_enr,ifelse(yr2003_isced6_enr>0,yr2003_isced6_enr,ifelse(yr2002_isced6_enr>0,yr2002_isced6_enr,ifelse(yr2001_isced6_enr>0,yr2001_isced6_enr,ifelse(yr2000_isced6_enr>0,yr2000_isced6_enr,0)))))))))))))))))))))) %>%
  mutate(isced7_enr=ifelse(yr2020_isced7_enr>0,yr2020_isced7_enr,ifelse(yr2019_isced7_enr>0,yr2019_isced7_enr,ifelse(yr2018_isced7_enr>0,yr2018_isced7_enr,ifelse(yr2017_isced7_enr>0,yr2017_isced7_enr,ifelse(yr2016_isced7_enr>0,yr2016_isced7_enr,ifelse(yr2015_isced7_enr>0,yr2015_isced7_enr,ifelse(yr2014_isced7_enr>0,yr2014_isced7_enr,ifelse(yr2013_isced7_enr>0,yr2013_isced7_enr,ifelse(yr2012_isced7_enr>0,yr2012_isced7_enr,ifelse(yr2011_isced7_enr>0,yr2011_isced7_enr,ifelse(yr2010_isced7_enr>0,yr2010_isced7_enr,ifelse(yr2009_isced7_enr>0,yr2009_isced7_enr,ifelse(yr2008_isced7_enr>0,yr2008_isced7_enr,ifelse(yr2007_isced7_enr>0,yr2007_isced7_enr,ifelse(yr2006_isced7_enr>0,yr2006_isced7_enr,ifelse(yr2005_isced7_enr>0,yr2005_isced7_enr,ifelse(yr2004_isced7_enr>0,yr2004_isced7_enr,ifelse(yr2003_isced7_enr>0,yr2003_isced7_enr,ifelse(yr2002_isced7_enr>0,yr2002_isced7_enr,ifelse(yr2001_isced7_enr>0,yr2001_isced7_enr,ifelse(yr2000_isced7_enr>0,yr2000_isced7_enr,0)))))))))))))))))))))) %>%
  mutate(isced8_enr=ifelse(yr2020_isced8_enr>0,yr2020_isced8_enr,ifelse(yr2019_isced8_enr>0,yr2019_isced8_enr,ifelse(yr2018_isced8_enr>0,yr2018_isced8_enr,ifelse(yr2017_isced8_enr>0,yr2017_isced8_enr,ifelse(yr2016_isced8_enr>0,yr2016_isced8_enr,ifelse(yr2015_isced8_enr>0,yr2015_isced8_enr,ifelse(yr2014_isced8_enr>0,yr2014_isced8_enr,ifelse(yr2013_isced8_enr>0,yr2013_isced8_enr,ifelse(yr2012_isced8_enr>0,yr2012_isced8_enr,ifelse(yr2011_isced8_enr>0,yr2011_isced8_enr,ifelse(yr2010_isced8_enr>0,yr2010_isced8_enr,ifelse(yr2009_isced8_enr>0,yr2009_isced8_enr,ifelse(yr2008_isced8_enr>0,yr2008_isced8_enr,ifelse(yr2007_isced8_enr>0,yr2007_isced8_enr,ifelse(yr2006_isced8_enr>0,yr2006_isced8_enr,ifelse(yr2005_isced8_enr>0,yr2005_isced8_enr,ifelse(yr2004_isced8_enr>0,yr2004_isced8_enr,ifelse(yr2003_isced8_enr>0,yr2003_isced8_enr,ifelse(yr2002_isced8_enr>0,yr2002_isced8_enr,ifelse(yr2001_isced8_enr>0,yr2001_isced8_enr,ifelse(yr2000_isced8_enr>0,yr2000_isced8_enr,0)))))))))))))))))))))) %>%
   mutate(natpop_est=ifelse(yr2020_nat_pop>0,yr2020_nat_pop,ifelse(yr2019_nat_pop>0,yr2019_nat_pop,ifelse(yr2018_nat_pop>0,yr2018_nat_pop,ifelse(yr2017_nat_pop>0,yr2017_nat_pop,ifelse(yr2016_nat_pop>0,yr2016_nat_pop,ifelse(yr2015_nat_pop>0,yr2015_nat_pop,ifelse(yr2014_nat_pop>0,yr2014_nat_pop,ifelse(yr2013_nat_pop>0,yr2013_nat_pop,ifelse(yr2012_nat_pop>0,yr2012_nat_pop,ifelse(yr2011_nat_pop>0,yr2011_nat_pop,ifelse(yr2010_nat_pop>0,yr2010_nat_pop,ifelse(yr2009_nat_pop>0,yr2009_nat_pop,ifelse(yr2008_nat_pop>0,yr2008_nat_pop,ifelse(yr2007_nat_pop>0,yr2007_nat_pop,ifelse(yr2006_nat_pop>0,yr2006_nat_pop,ifelse(yr2005_nat_pop>0,yr2005_nat_pop,ifelse(yr2004_nat_pop>0,yr2004_nat_pop,ifelse(yr2003_nat_pop>0,yr2003_nat_pop,ifelse(yr2002_nat_pop>0,yr2002_nat_pop,ifelse(yr2001_nat_pop>0,yr2001_nat_pop,ifelse(yr2000_nat_pop>0,yr2000_nat_pop,0)))))))))))))))))))))) %>%
  rowwise() %>%
  filter(!isced6_ref_yr+isced7_ref_yr+isced8_ref_yr==0) %>%
  select(country,isced6_enr,isced6_ref_yr,isced7_enr,isced7_ref_yr,isced8_enr,isced8_ref_yr,natpop_est,natpop_ref_yr) 
university_enrollment_data 
```

After selecting out the annualized columns for each of the four population estimates, we are left with 8 columns noting the estimate and reference year for the most recent year there is available population data. 

In addition to the rows that were removed due to the there being no provided isced 6, 7, or 8 enrollment estimates across the 20-year window of investigation, we will also need to remove the rows that represent aggregated data across regions or groups of countries (i.e., what the EdStats database refers to as "aggregates." These include the designations: 

* "Arab World"
* "Caribbean small states"
* "Central Europe and the Baltics"
* "Early-demographic dividend"
* "East Asia & Pacific"
* "East Asia & Pacific (excluding high income)"
* "East Asia & Pacific (IDA & IBRD countries)"
* "Euro area"
* "Europe & Central Asia"
* "Europe & Central Asia (excluding high income)"
* "Europe & Central Asia (IDA & IBRD countries)"
* "European Union"
* "Fragile and conflict affected situations"
* "Heavily indebted poor countries (HIPC)"
* "High income"
* "IBRD only"
* "IDA & IBRD total"
* "IDA blend"
* "IDA only"
* "IDA total"
* "Late-demographic dividend"
* "Latin America & Caribbean"
* "Latin America & Caribbean (excluding high income)"
* "Latin America & the Caribbean (IDA & IBRD countries)"
* "Least developed countries: UN classification"
* "Low & middle income"
* "Low income"
* "Lower middle income"
* "Middle East & North Africa"
* "Middle East & North Africa (excluding high income)"
* "Middle East & North Africa (IDA & IBRD countries)"
* "Middle income"
* "North America"
* "OECD members"
* "Other small states"
* "Pacific island small states"
* "Post-demographic dividend"
* "Pre-demographic dividend"
* "Small states"
* "South Asia"
* "South Asia (IDA & IBRD)"
* "Sub-Saharan Africa"
* "Sub-Saharan Africa (excluding high income)"
* "Upper middle income"
* "World"

```{r}

```

Now, we can make a new column that combines the ISCED 6, 7, and 8 enrollee estimates called `uni_enr_tot`

## Spatially Joining Our University Enrollment Data

map gap

## Writing the Final Data File


